\subsection{Physical/Real-world Environment}
The real-world environment that the user will be tracked in is 10'x30'.
The user is provided with a Head-Mounted Display and two 6 Degree of Freedom (6DOF) devices with 11 buttons each (Wiimotes).
The tracking of the head and each Wiimote is done with a Vicon system placed around the tracking area.

\subsection{Virtual Environment}
The virtual environment is an empty and infinite 3D canvas for the user to create a virtual world.
This allows the user to create any object, building, landscape, or geometrical feature that is possible, with any size imaginable.
Since the user is creating a world, there are no sounds, animations, or simulation effects in place to begin with.
However, the user may create any item within the world, which can be utilized to create moving objects, 3D sounds, and simulation effects.
For instance, the user can create a car that moves along a street, which associated engine and tire noise as it moves.
The user could also create the ground, and say that objects must ``rest'' upon the ground (simulating gravity).

\subsection{Interaction}

\subsubsection{Selection}
Object selection is a crucial task for most of the features within this project.
Several selection selection methods are provided, which can be selected based on the users preference.
\begin{itemize}
	\item Simple Virtual Hand
	\item Simple Ray-Casting
	\item PORT
\end{itemize}

\paragraph{Simple Virtual Hand}
A virtual hand will be co-located with the user's real hand.
The user will not be able grasp any objects out of their reach, and must navigate to manipulate anything.
This method of selection is the easiest to understand and use, but affords the least flexibility.

\paragraph{Simple Ray-Casting}
Much like Simple Virtual Hand, however the user is able to reach out to infinity, or until an object is encountered.
This affords the user to be able to manipulate objects that are very far out of reach, but requires the user to learn to take advantage of this.
We believe this will require very little cognitive overhead, and should not cause problems for any user.
As such, this will be the default selection method.

\paragraph{PORT}
The user can create a 3D selection box, where all objects within the box become selected.
This selection method provides the most flexibility, especially within our application, however the cognitive overhead on the user is much higher.
Once a user is proficient with the system, we believe this will be the most used selection method.

\subsubsection{Manipulation}
There are several manipulation techniques provided.
\begin{itemize}
	\item Single-Object Manipulation
		\subitem Creation
		\subitem Deletion
		\subitem Translation
		\subitem Rotation
		\subitem Scaling
		\subitem Coloring
		\subitem Texturing
	\item Multi-Object Manipulation
		\subitem Boolean Operations
		\subitem Grouping
		\subitem Deletion
	\item World Manipulation
		\subitem Scale-the-World
		\subitem Light creation/manipulation
		\subitem Sound creation/manipulation
\end{itemize}

\paragraph{Single-Object Manipulation}
This subcategory of manipulation is dedicated to a user manipulating one object at a time.
Creation and deletion will be done through a menu (described in System Control, below), however deletion will require an object to be selected first.
Translation, rotation, and scaling will all be performed with button interaction on the Wiimote, after an object is selected.
Scaling is unique, as it requires bimanual input.
The user must select and object, press buttons on both Wiimotes, and move both hands for the object to be scaled.
The actual motion will be determined by the hand movement while interaction button is being held down.
Coloring and texturing will also be performed through a menu (again, see below), and will also require an object to be selected first.

\paragraph{Multi-Object Manipulation}
There are three boolean operations using multiple objects provided.  Boolean operations can be performed when there are overlapping portions of multiple selected objects.
\begin{enumerate}
	\item Union
	\subitem When the user selects the union operation and multiple objects are selected, it creates a single object made up of all the objects that were selected.
	\item Intersection
	\subitem When intersection is selected, the non-overlapping portions of the selected objects will be removed, leaving a single object made up of only the intersecting portion.
	\item Subtraction
	\subitem This operation is limited to two selected objects.  When subtraction is selected, the user chooses a primary object, and the overlapping portion of the primary object is removed.  This operation leaves two objects, however the primary object is now missing the overlapped portion.
\end{enumerate}

Grouping objects allows the user create a single object from a group of selected objects.
Unlike the boolean operations, no logic is performed on the group besides making them behave as a single object.
The grouped objects, for all intents and purposes, behave as a single object, all the single object manipulations above work on a grouped objects.
One benefit grouped objects provide over the boolean operations, is that it can be undone.
Multiple objects can be grouped, manipulated, ungrouped, and manipulated independently.
Grouping objects will be performed through the menu described below.

Deletion is the same as single-object deletion, however it allows the user to delete multiple, unconnected objects (as long as all are selected).

\paragraph{World Manipulation}
When the user grabs the air with both hands, and performs the scaling operation, the entire world will be scaled up or down, according to the user's movement.
This allows the user to navigate more easily, as well as create very large structures within the virtual environment without too much effort (simply scale the world down, create a normal object, and scale the world back to normal size).

Light creation and manipulation allows the user to create lights, move them, and change aspects of the lights to suit the application (color, attenuation, direction, etc...).\footnote{Technical note: We are using OpenGL, so the number of lights in the world is limited to 8.}
The same ability exists for sounds.
The user can create a sound, attach it to an object, and the sound is then created from a specific point in space.

\subsubsection{Navigation}
Navigation is another crucial feature.
Since the world is infinite, there must be a sensible way to navigate, otherwise the world will be limited to the size of the tracked area.
This will be handling by applying the Scale-the-World technique listed above.
Since the user can scale the entire world down, they can make everything smaller, making their steps much larger.
This method forsakes some interaction fidelity for the benefit of an infinite world.

\subsubsection{System Control}
As mentioned above, a menu will be present.
The menu is created in 3D space where the user's hand is when they press the menu key on the right-hand Wiimote.
The menu is a collection of categories laid out in tabs, with buttons under each tab for the functions available in that category.
The categories provided are:
\begin{itemize}
	\item Objects
	\subitem Allows the creation of default objects (sphere, cube, cone, etc...)
	\item Materials
	\subitem Contains a collection of colors and textures to apply to objects
	\item Tools
	\subitem All of the advanced interaction methods listed above
	\item File Operations
	\subitem This category is unique, as it doesn't pertain to editing the world.  This category contains operations to save the existing world to file, load a file as an existing world, export an object to use again later, and load an object that was previously exported.
\end{itemize}